Automated detection \& characterization of long-period transits in the \kepler\ archive

### 2015-12-21 document/ms.tex
more step models

Many of the most dynamically important planets have orbits longer than the
baseline of existing transit surveys (\kepler, \KT).
Future surveys (\tess, \plato) are planned to have shorter continuous coverage
that even habitable zone planets around M-dwarfs will only present a single
transit event.
Searches for these long-period transiting planets are plagued by false
signals---especially when pushed to low signal-to-noise---and statistical
studies of their population are complicated by weak constraints on the
physical parameters of the system and high rates of false positives.
We develop and present a computationally expensive but tractable method of
searching for single transits using supervised classification methods from
the machine learning literature.
For each star, we train several random forest classifiers on simulated signals
injected into different subsets of the data.
These models are evaluated on the raw photometry to assign a transit
probability at each time.
As a proof of concept, we apply this method to 3500 light curves from the
\kepler\ archival dataset and discover a previously unknown single transit
candidate.
Assuming a bound Keplerian orbit and using an informative prior on the
eccentricity, we measure a radius of $2\,R_\mathrm{J}$ and derive a weak
constraint on the orbital period.

@@

In \sect{est}, we extrapolate a recent model of the distribution of exoplanets
to the long periods considered in this \paper.
Using an approximate but realistic model for the detection efficiency of a
search for single transits, we estimate that $\sim 60$ single transit events
should be detectable in the archival \kepler\ dataset.
In \sect{data}, we describe the data and outline the structure exploited by
our transit search procedure.
In \sect{rfc}, we briefly describe the Random Forest classification framework
and in \sect{search} we outline the steps used to apply this model for transit
search.
This method requires the setting of many tuning parameters and the
optimization of these choices is both computationally and intellectually
challenging so in \sect{tuning} we discuss some steps in this direction.
In \sect{demo}, we demonstrate the feasibility of this method, present a
single transit discovery, and indicate some interesting weaknesses of the
method.
In \sectionname s~\sectref{params} we describe the parameter estimation that
is possible given a single transit.

@@

\section{Some appendix}

>>>>

Hi.

@@

@@

\section{Supervised classification}

% In \sect{est}, we extrapolate a recent model of the distribution of exoplanets
% to the long periods considered in this \paper.
% Using an approximate but realistic model for the detection efficiency of a
% search for single transits, we estimate that $\sim 60$ single transit events
% should be detectable in the archival \kepler\ dataset.
% In \sect{data}, we describe the data and outline the structure exploited by
% our transit search procedure.
% In \sect{rfc}, we briefly describe the Random Forest classification framework
% and in \sect{search} we outline the steps used to apply this model for transit
% search.
% This method requires the setting of many tuning parameters and the
% optimization of these choices is both computationally and intellectually
% challenging so in \sect{tuning} we discuss some steps in this direction.
% In \sect{demo}, we demonstrate the feasibility of this method, present a
% single transit discovery, and indicate some interesting weaknesses of the
% method.
% In \sectionname s~\sectref{params} we describe the parameter estimation that
% is possible given a single transit.
